Title here

### 2016-08-14 portfolio/text/ms.Rmd
Develop text

@@

[@standevelopmentteam2015]

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/fig1-jk.pdf}
\caption{Caption here}
\label{fig:ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Caption here}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Caption here}
\label{fig:across}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Caption here}
\label{fig:within}
\end{center}
\end{figure}

>>>>

# Abstract

@@

[@standevelopmentteam2015]
[@rcoreteam2016]

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/fig1-jk.pdf}
\caption{
Trends in revenue and diversification over time.
(A) Map of fishing regions in Alaska, USA.
(B) Total revenue in billions of 20XX U.S. dollars from `r range_yrs[1]` to
`r range_yrs[2]` for multiple (grey) and single (blue) permit holders.
(C) Proportion of single permit holders for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the
`r n_jacknifed` top species groups (thin lines).
(D) Mean effective diversity of species fished (Simpson's diversity index) 
for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the
`r n_jacknifed` top species groups (thin lines).
}
\label{fig:ts}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Adding permits reduces risk.
Two examples of expected revenue variability 
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(light blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (dark blue).
On the y-axis, dots and lines represent posterior median and 50\%
credible intervals.}
\label{fig:spokes}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability.pdf}
\caption{Fishing strategies with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common strategies.
Thick black line, dark, and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the heirarchical model.
}
\label{fig:across}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of generalizing and specializing from year to year for
individual permit holders across the `r nstr` most common strategies.}
\label{fig:within}
\end{center}
\end{figure}
